---
title: "OSM Mining"
author: "Kate Lyons"
date: "9/13/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Getting data from Open Street Map! 

Open Street Map (OSM) is an open source data base of a TON of spatial data. We're going to use it to get shape files of the different Vienna districts we've collected data on. We'll use the [osmdata](https://github.com/ropensci/osmdata) library to access OSM's Overpass API.

See LL survey areas [here](https://www.google.com/maps/d/u/0/edit?mid=11PGdR_KN4RS52y3d71QgWdsOeDcl_6aS&ll=48.20932199596231%2C16.342377515237057&z=15).

```{r Libraries}
library(ggplot2)
library(sf)
library(osmdata)
library(osmar)
library(prettymapr)
library(tidyverse)
library(sp)
library(ggmap)
library(splancs)
library(rgeos)
library(rgdal)
library(tmap)
library(geojsonR)
library(plyr)

# Set API key for ggmap
register_google(key = "AIzaSyCTlb6z8LgAxNrx6565KuSoUm1HogxkmKE")

# Load test data for filtering
load("/Users/katelyons/Documents/ELLViA/Data/1st District/instaOnlyinnere.RData")

load("/Users/katelyons/Documents/ELLViA/Data/8th District/eighthDistrictInsta.RData")

load("~/Documents/ELLViA/Data/16th District/ottarkring.RData")

load("/Users/katelyons/Documents/ELLViA/Data/18th District/währing.RData")

load("/Users/katelyons/Documents/ELLViA/Data/19th District/döbling.RData")

load("/Users/katelyons/Documents/ELLViA/Data/21st District/instaOnly21.RData")

instaData <- list(instaOnlyinnere, eighthDistrictInsta, ottarkring, währing, döbling, instaOnly21)
```

## Getting boundaries

Going to use the OSM API to grab spatial data on the region and subset to the specific district we want using the OSM ID field. Help on this from [here](https://altran-data-analytics.netlify.app/2017/10/10/2017-10-10-creating-maps-with-r-and-openstreetmap/).

The method of retrival / processing depends on if they have the ability to be converted to an sf object. If the district is in OSM as a boundary object, we can grab the polygon directly, if it's just there as a bounding box, we have to covert ourselves another way. 

```{r Get boundaries in simple format polygon}
# Get boundaries for specific region
# JosefstadtBoundaries <- opq(bbox = 'Josefstadt Wien')

# Start at the admin level!
wien9Boundaries <- opq(bbox = 'Wien Austria') %>%
  add_osm_feature(key = 'admin_level', value = '9') %>% 
  osmdata_sf %>% unique_osmdata

# Might not need this:
# wien10Boundaries <- opq(bbox = 'Wien Austria') %>%
#   add_osm_feature(key = 'admin_level', value = '10') %>% 
#   osmdata_sf %>% unique_osmdata

# Subset to area of interest for testing
# innerePoly <- wien10Boundaries$osm_multipolygons %>% filter(osm_id == '5264583')

innerePoly <- wien9Boundaries$osm_multipolygons %>% filter(osm_id == '1990592')

josefstadtPoly <- wien9Boundaries$osm_multipolygons %>% filter(osm_id == '1990593')

ottakringPoly <- wien9Boundaries$osm_multipolygons %>% filter(osm_id == '1991441')

waehringPoly <- wien9Boundaries$osm_multipolygons %>% filter(osm_id == '1990600')

doeblingPoly <- wien9Boundaries$osm_multipolygons %>% filter(osm_id == '1991435')

floridsdorfPoly <- wien9Boundaries$osm_multipolygons %>% filter(osm_id == '1991437')

# josefstadtPoly <- wienBoundaries$osm_multipolygons %>% filter(osm_id == '240118849')
```

Because of a weird discrepancy between the type of projection of the OSM shapefile and Google Maps, you have to do a couple of transformations before you can map with ggmap. Help from [here](https://stackoverflow.com/a/50844502/7451811)!

```{r How to map the area you get from OSM with sf}
# Create list of dfs
districts <- list(innerePoly, josefstadtPoly, ottakringPoly, waehringPoly, doeblingPoly, floridsdorfPoly)

# Transform nc to EPSG 3857 (Pseudo-Mercator, what Google uses)
districts_3857 <- lapply(districts, function(x) st_transform(x, 3857))

# View(districts_3857[1])

# ott_3857 <- st_transform(poly8th, 3857)
# eigth_3857 <- st_transform(poly8th, 3857)

# ott_map <- get_map("Ottakring Wien", zoom = 12, source = "google")
# ott_map <- get_map("Josefstadt Wien", zoom = 13, source = "google")

# Get a map of Vienna:
wien_map <- get_map("Brigittenau Wien Austria", zoom = 11, source = "google")

# Define a function to fix the bbox to be in EPSG:3857
ggmap_bbox <- function(wien_map) {
  if (!inherits(wien_map, "ggmap")) stop("map must be a ggmap object")
  # Extract the bounding box (in lat/lon) from the ggmap to a numeric vector, 
  # and set the names to what sf::st_bbox expects:
  map_bbox <- setNames(unlist(attr(wien_map, "bb")), 
                       c("ymin", "xmin", "ymax", "xmax"))

  # Coonvert the bbox to an sf polygon, transform it to 3857, 
  # and convert back to a bbox (convoluted, but it works)
  bbox_3857 <- st_bbox(st_transform(st_as_sfc(st_bbox(map_bbox, crs = 4326)), 3857))

  # Overwrite the bbox of the ggmap object with the transformed coordinates 
  attr(wien_map, "bb")$ll.lat <- bbox_3857["ymin"]
  attr(wien_map, "bb")$ll.lon <- bbox_3857["xmin"]
  attr(wien_map, "bb")$ur.lat <- bbox_3857["ymax"]
  attr(wien_map, "bb")$ur.lon <- bbox_3857["xmax"]
  wien_map
}

# Use the function:
wien_map <- ggmap_bbox(wien_map)

ggmap(wien_map) + 
  coord_sf(crs = st_crs(3857)) + # force the ggplot2 map to be in 3857
  lapply(districts_3857, function(x) geom_sf(data = x, aes(fill = name, alpha = 0.6), inherit.aes = FALSE, show.legend = FALSE)) 

# Try to add label...
# test <- st_transform(innerePoly, 3857)
# ggmap(wien_map) + 
#   coord_sf(crs = st_crs(3857)) + # force the ggplot2 map to be in 3857
#   # geom_sf(data = test, aes(fill = name, alpha = 0.6)) + 
#   geom_sf_text(aes(label = NAME))
```

## Filtering tweets based on boundaries + graphing!:

To be able to see what tweets fall in the exact district borders, we'll use the st_intersects function. To do this we need to convert our latitute and longitude coordinates to an sf object first. 

Help on using st_intersects from [here](https://gis.stackexchange.com/questions/282750/identify-polygon-containing-point-with-r-sf-package/318629#318629)!

```{r}
# First only keep records where we have a coordinate (bc st_as_sf doesn't like NAs!):
districts_cords <- lapply(instaData, function(x) subset(x, (!is.na(x$lng)) & (!is.na(x$lat))))

# ott_tweet_cords <- subset(ottarkring, (!is.na(ottarkring$lng)) & (!is.na(ottarkring$lat)))
# innere_tweet_cords <- subset(instaOnlyinnere, (!is.na(instaOnlyinnere$lng)) & (!is.na(instaOnlyinnere$lat)))

# Convert to sf object
districts_cords_sf <- lapply(districts_cords, function(x) sf::st_as_sf(x, coords=c("lng","lat"), crs=4326))

# ott_tweet_cords_sf <- sf::st_as_sf(ott_tweet_cords, coords=c("lng","lat"), crs=4326)
# innere_tweet_cords_sf <- sf::st_as_sf(innere_tweet_cords, coords=c("lng","lat"), crs=4326)

# Find the intersection between the two files
districts_int <- mapply(function(x,y) sf::st_intersects(x, y), districts_cords_sf,districts)

# ott_int <- sf::st_intersects(ott_tweet_cords_sf, ottakringPoly)
# innere_int <- sf::st_intersects(innere_tweet_cords_sf, innerePoly)

# Add this on as a column in the original data frames to tag them in/out
# Had such a hard time with this, finally figured it out from here: https://stackoverflow.com/a/50949909/7451811
districts_tagged <- Map(function(x, y) {
  x$in_district <- as.character(y)
  x
},
  districts_cords, 
  districts_int)

# ott_tweet_cords$in_district <- as.character(ott_int)
# innere_tweet_cords$in_district <- as.character(innere_int)

# Rename values so it's easier to read!
districts_taggedII <- lapply(districts_tagged, function(x) dplyr::mutate(x, in_district = plyr::revalue(in_district, c("1" = "Yes","integer(0)" = "No"))))

# ott_tweet_cords$in_district <- ott_tweet_cords$in_district %>%
#   revalue(c("1" = "Yes","integer(0)" = "No"))
# innere_tweet_cords$in_district <- innere_tweet_cords$in_district %>%
#   revalue(c("1" = "Yes","integer(0)" = "No"))
  
# Subset to only in district:
district_posts <- lapply(districts_taggedII, function(x) subset(x, x$in_district == 'Yes'))

# ott_tweets <- subset(ott_tweet_cords, ott_tweet_cords$in_district == 'Yes')

# Test!
table(district_posts[[1]]$in_district)
table(district_posts[[3]]$in_district)
```

## Creating layered maps

To layer the tweet data on top of our district boundary, we need to convert it to the same Pseudo-Mercator format.


```{r Map}
# Subset to only in district:
# ott_tweets <- subset(ott_tweet_cords, ott_tweet_cords$in_district == 'Yes')
# innere_tweets <- subset(innere_tweet_cords, innere_tweet_cords$in_district == 'Yes')

# Have to follow a similar protocol above I think to be able to map...

# Convert to sf object

# Step 1:
district_posts_4326 <- lapply(district_posts, function(x) sf::st_as_sf(x, coords=c("lng","lat"), crs=4326))

# Step 2:
# Transform tweet dots to EPSG 3857 (Pseudo-Mercator, what Google uses)
district_posts_3857 <- lapply(district_posts_4326, function(x) st_transform(x, 3857))
# ott_tweets_4326 <- sf::st_as_sf(ott_tweets, coords=c("lng","lat"), crs=4326)

# Transform ott tweet dots to EPSG 3857 (Pseudo-Mercator, what Google uses)
# ott_tweets_3857 <- st_transform(ott_tweets_4326, 3857)

# Try to layer:
ggmap(wien_map) +
  coord_sf(crs = st_crs(3857)) + # force the ggplot2 map to be in 3857
  geom_sf(data = district_posts_3857[[2]], aes(fill = name, alpha = 0.6), inherit.aes = FALSE, show.legend = FALSE) +
  geom_sf(data = district_posts_3857[[3]], aes(fill = name, alpha = 0.6), inherit.aes = FALSE, show.legend = FALSE) +
  geom_sf(data = districts_3857[[2]], aes(fill = name, alpha = 0.6), inherit.aes = FALSE, show.legend = FALSE) +
  geom_sf(data = districts_3857[[3]], aes(fill = name, alpha = 0.6), inherit.aes = FALSE, show.legend = FALSE)


# Took too long (too big)
# ggmap(wien_map) + 
#   coord_sf(crs = st_crs(3857)) + # force the ggplot2 map to be in 3857
#   lapply(district_posts_3857, function(x) geom_sf(data = x, aes(fill = name, alpha = 0.6), inherit.aes = FALSE, show.legend = FALSE)) 

# ggmap(ott_map) +
#   coord_sf(crs = st_crs(3857)) + # force the ggplot2 map to be in 3857
#   geom_sf(data = ott_3857, aes(fill = name, alpha = 0.6), inherit.aes = FALSE, show.legend = FALSE) +
#   geom_sf(data = ott_tweets_3857, aes(fill = name, alpha = 0.6), inherit.aes = FALSE, show.legend = FALSE)
```

## Alternative method

This is another straightforward method that gives you the district polygon in a different format. Actually works nicer than the above method because you can just use geom_path (very important to use geom_path because it follows the order of the points as they are presented, which means we get a nice boundary line!)

Method to get the polygon from osmdata's vignette. 

```{r Build query - test with Ottakring + map}
# Get polygon of boundary...

# List of places we want BBs for
names <- list("Innere Stadt Wien", "Josefstadt Wien", "Ottakring Wien", "Währing Wien", "Floridsdorf, Wien")

# "Döbling Wien"
# Get bounding boxes
bbs <- lapply(names, function(x) getbb(x, format_out = "polygon"))

# Get lat and lons for these
bbCoordsDFs <- lapply(bbs, function(x) data.frame(Longitude = as.vector(x[[1]][,1]), Latitude = as.vector(x[[1]][,2])))

# Have to do this separately bc it's different
döblingBB <- getbb("Döbling Wien", format_out = "polygon")
döblingBBdf <- data.frame(Longitude = döblingBB[,1], Latitude = döblingBB[,2])

# Add to list of dfs 
allbbCoordsDFs <- c(list(döblingBBdf), bbCoordsDFs)

# innerePolyBB <- getbb ("Innere Stadt Wien", format_out = "polygon")
# ottakringPolyBB <- getbb ("Ottakring Wien", format_out = "polygon")
# JosefstadtPolyBB <- getbb ("Josefstadt Wien", format_out = "polygon")
# testBB <- getbb("Döbling Wien", format_out = "polygon")
# 
# View(data.frame(Longitude = testBB[,1], Latitude = testBB[,2]))

# JosefstadtCoordsDF = data.frame(Longitude = as.vector(JosefstadtPolyBB[[1]][,1]), Latitude = as.vector(JosefstadtPolyBB[[1]][,2]))

# instaOnlyinnere, eighthDistrictInsta, ottarkring, währing, döbling, instaOnly21

# class (ottakring); head (ottakring [[1]])

# lon <- as.vector(ottakring[[1]][,1])
# lat <- as.vector(ottakring[[1]][,2])


# Map to see if this actually works... kind of?

# get_googlemap("Friedhof Wien Ottakring", zoom = 13) %>% ggmap() + geom_path(data = ottakringCoordsDF, aes(x = Longitude, y = Latitude), color = 'navy')
# 
# get_googlemap("Innere Stadt Wien", zoom = 14) %>% ggmap() + geom_path(data = innereCoordsDF, aes(x = Longitude, y = Latitude), color = 'navy')

# MAP ALL THESE !
get_googlemap("Brigittenau Wien Austria", zoom = 11) %>% ggmap() + lapply(allbbCoordsDFs, function(x) geom_path(data = x, aes(x = Longitude, y = Latitude), color = 'navy'))
  
  # data = ottakringCoordsDF, aes(x = Longitude, y = Latitude), color = 'navy')

```

Now let's put this all together!

```{r Combine with above work to filter out points that don't exist in the boundary}

get_googlemap("Brigittenau Wien Austria", zoom = 11) %>% ggmap() + lapply(allbbCoordsDFs, function(x) geom_path(data = x, aes(x = Longitude, y = Latitude), color = 'navy')) +
  lapply(district_posts, function(x) geom_point(data = x, aes(x = lng, y = lat), color = 'black', alpha = 0.5))


# get_googlemap("Friedhof Wien Ottakring", zoom = 13) %>% ggmap() + 
#   geom_path(data = ottakringCoordsDF, aes(x = Longitude, y = Latitude), color = 'navy') +
#   geom_point(data = ott_tweets, aes(x = lng, y = lat), color = 'black')
# 
# get_googlemap("Innere Stadt Wien", zoom = 14) %>% ggmap() + 
#   geom_path(data = innereCoordsDF, aes(x = Longitude, y = Latitude), color = 'navy') +
#   geom_point(data = innere_tweets, aes(x = lng, y = lat), color = 'black', alpha = 0.5)
# 
# # All together
# get_googlemap("Neulerchenfeld 1160 Vienna, Austria", zoom = 12) %>% ggmap() + 
#   geom_path(data = ottakringCoordsDF, aes(x = Longitude, y = Latitude), color = 'navy') +
#   geom_point(data = ott_tweets, aes(x = lng, y = lat), color = 'black') +
#   geom_path(data = innereCoordsDF, aes(x = Longitude, y = Latitude), color = 'navy') +
#   geom_point(data = innere_tweets, aes(x = lng, y = lat), color = 'black', alpha = 0.5)

```


```{r}
JosefstadtPolyBB <- getbb ("Josefstadt Wien", format_out = "polygon")

JosefstadtCoordsDF = data.frame(Longitude = as.vector(JosefstadtPolyBB[[1]][,1]), Latitude = as.vector(JosefstadtPolyBB[[1]][,2]))


get_googlemap("Josefstadt Wien", zoom = 14) %>% ggmap() + 
  geom_path(data = JosefstadtCoordsDF, aes(x = Longitude, y = Latitude), color = 'navy')

```


```{r}
# Save to CSV the cut files

allNames <- list("1 Innere Stadt", "8 Josefstadt", "16 Ottakring", "18 Währing", "19 Döbling", "21 Floridsdorf")

# Save:
library(rtweet)
setwd("/Users/katelyons/Documents/ELLViA/Data/District Posts")

mapply(function(x,y) save_as_csv(x, y, prepend_ids = TRUE, na = "", fileEncoding = "UTF-8"), district_posts, allNames)

# Save as R Data:
save(district_posts, file = 'District Posts.RData')
# mapply(function(x,y) save(x, file = paste(y, ".RData", sep = "")), district_posts, allNames)

# save_as_csv(innere_tweets, '1st District Bounded Instagram', prepend_ids = TRUE, na = "", fileEncoding = "UTF-8")
# 
# setwd("/Users/katelyons/Documents/ELLViA/Data/16th District")
# save_as_csv(ott_tweets, '16th District Bounded Instagram', prepend_ids = TRUE, na = "", fileEncoding = "UTF-8")
# 
# dfchunk[[1]]
# district_posts
```


```{r}
# # Try to fix encoding issue...
# 
# # split innere_tweets in two
# n <- 2
# dfchunk <- split(innere_tweets, factor(sort(rank(row.names(innere_tweets))%%n)))
# 
# save_as_csv(dfchunk[[1]], '1st District Bounded Instagram I', prepend_ids = TRUE, na = "", fileEncoding = "UTF-8")
# 
# save_as_csv(dfchunk[[2]], '1st District Bounded Instagram II', prepend_ids = TRUE, na = "", fileEncoding = "UTF-8")

```