---
title: "ellvia_maps"
author: "Kate Lyons"
date: "2/24/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Creating nice maps of ELLViA Instagram data

```{r Load in libraries}
# Make sure you have the right packages!
packs = c("tidyverse","tidytext","stringr","ggplot2","ggmap",
          "scales","ggrepel","lubridate","purrr","broom", "tidylo", "fuzzyjoin",
          "sf", "osmdata", "osmar", "prettymapr", "sp", "splancs", "rgeos",
          "rgdal", "tmap", "geojsonR")
lapply(packs, library, character.only=T)
```

```{r Load in data}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
setwd('..')
district_unigram_wlo <- read.csv("data/processed/district_unigram_wlo.csv")
district_unigram_freq <- read.csv("data/processed/district_unigram_freq.csv")
```

```{r Get map}
# Set up Google Maps API stuff:
register_google(key = "AIzaSyCTlb6z8LgAxNrx6565KuSoUm1HogxkmKE")

# Get wien map!
wien_map <- get_map("Brigittenau Wien Austria", zoom = 11, source = "google")
ggmap(wien_map)
```

```{r Put wlo on map!}
# Map!!
district_unigram_wlo$lng<-as.numeric(district_unigram_wlo$lng)
district_unigram_wlo$lat<-as.numeric(district_unigram_wlo$lat)
lon <- district_unigram_wlo$lng
lat <- district_unigram_wlo$lat

ggmap(wien_map) + geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_label_repel(data = district_unigram_wlo, aes(x = lon, y = lat, label = unigrams),
  size = 3, max.overlaps = getOption("ggrepel.max.overlaps", default = 150)) 

```

```{r Put freq on map!}
# Map!!
district_unigram_freq$lng<-as.numeric(district_unigram_freq$lng)
district_unigram_freq$lat<-as.numeric(district_unigram_freq$lat)
lon <- district_unigram_freq$lng
lat <- district_unigram_freq$lat

ggmap(wien_map) + geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_label_repel(data = district_unigram_freq, aes(x = lon, y = lat, label = unigrams), size = 3, max.overlaps = getOption("ggrepel.max.overlaps", default = 150)) 

```

```{r Check Mission data for counts - get data}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
setwd('..')
terr <- read.csv("data/raw/mission_data/9_March_Mission_Data.csv")
insta <- read.csv("data/raw/mission_data/Col_Sep_INSTACORPUS.csv")
```

```{r Check Mission data for counts - fuzzyjoin}
pairsdf <- terr %>%
  geo_inner_join(insta, unit='km',distance_col="distance", max_dist = "0.018288")

# How much overlap?
pairsdf %>% n_distinct('SIGN_ID', na.rm=TRUE)
terr %>% n_distinct('SIGN_ID') # 1031
View(pairsdf%>% select('SIGN_ID') %>% distinct())
```


Going to use the OSM API to grab spatial data on the region and subset to the specific district we want using the OSM ID field. Help on this from [here](https://altran-data-analytics.netlify.app/2017/10/10/2017-10-10-creating-maps-with-r-and-openstreetmap/).

The method of retrival / processing depends on if they have the ability to be converted to an sf object. If the district is in OSM as a boundary object, we can grab the polygon directly, if it's just there as a bounding box, we have to covert ourselves another way. 
```{r Get OSM boundaries}
# Start at the admin level!
wien9Boundaries <- opq(bbox = 'Wien Austria') %>%
  add_osm_feature(key = 'admin_level', value = '9') %>% 
  osmdata_sf %>% unique_osmdata

# Now break down into districts:
# Subset to area of interest for testing

innerePoly <- wien9Boundaries$osm_multipolygons %>% filter(osm_id == '1990592')

josefstadtPoly <- wien9Boundaries$osm_multipolygons %>% filter(osm_id == '1990593')

ottakringPoly <- wien9Boundaries$osm_multipolygons %>% filter(osm_id == '1991441')

waehringPoly <- wien9Boundaries$osm_multipolygons %>% filter(osm_id == '1990600')

doeblingPoly <- wien9Boundaries$osm_multipolygons %>% filter(osm_id == '1991435')

floridsdorfPoly <- wien9Boundaries$osm_multipolygons %>% filter(osm_id == '1991437')
```

Because of a weird discrepancy between the type of projection of the OSM shapefile and Google Maps, you have to do a couple of transformations before you can map with ggmap. Help from [here](https://stackoverflow.com/a/50844502/7451811)!

```{r How to map the area you get from OSM with sf}
# Create list of dfs
districts <- list(innerePoly, josefstadtPoly, ottakringPoly, waehringPoly, doeblingPoly, floridsdorfPoly)

# Transform nc to EPSG 3857 (Pseudo-Mercator, what Google uses)
districts_3857 <- lapply(districts, function(x) st_transform(x, 3857))

# Get a map of Vienna:
wien_map <- get_map("Brigittenau Wien Austria", zoom = 11, source = "google")

# Define a function to fix the bbox to be in EPSG:3857
ggmap_bbox <- function(wien_map) {
  if (!inherits(wien_map, "ggmap")) stop("map must be a ggmap object")
  # Extract the bounding box (in lat/lon) from the ggmap to a numeric vector, 
  # and set the names to what sf::st_bbox expects:
  map_bbox <- setNames(unlist(attr(wien_map, "bb")), 
                       c("ymin", "xmin", "ymax", "xmax"))

  # Coonvert the bbox to an sf polygon, transform it to 3857, 
  # and convert back to a bbox (convoluted, but it works)
  bbox_3857 <- st_bbox(st_transform(st_as_sfc(st_bbox(map_bbox, crs = 4326)), 3857))

  # Overwrite the bbox of the ggmap object with the transformed coordinates 
  attr(wien_map, "bb")$ll.lat <- bbox_3857["ymin"]
  attr(wien_map, "bb")$ll.lon <- bbox_3857["xmin"]
  attr(wien_map, "bb")$ur.lat <- bbox_3857["ymax"]
  attr(wien_map, "bb")$ur.lon <- bbox_3857["xmax"]
  wien_map
}

# Use the function:
wien_map <- ggmap_bbox(wien_map)

ggmap(wien_map) + 
  coord_sf(crs = st_crs(3857)) + # force the ggplot2 map to be in 3857
  lapply(districts_3857, function(x) geom_sf(data = x, aes(fill = name, alpha = 0.6), inherit.aes = FALSE, show.legend = FALSE))
```

```{r Layering maps}
# Convert data to sf object

# Step 1:
district_unigram_wlo_4326 <- sf::st_as_sf(district_unigram_wlo, coords=c("lng","lat"), crs=4326)
  
# Step 2:
# Transform tweet dots to EPSG 3857 (Pseudo-Mercator, what Google uses)
district_unigram_wlo_3857 <- st_transform(district_unigram_wlo_4326, 3857)

# Layer?
ggmap(wien_map) + 
  coord_sf(crs = st_crs(3857)) + # force the ggplot2 map to be in 3857
  lapply(districts_3857, function(x) geom_sf(data = x, aes(fill = name, alpha = 0.6), inherit.aes = FALSE, show.legend = FALSE)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_label_repel(data = district_unigram_wlo_3857, aes(label = unigrams), size = 3, max.overlaps = getOption("ggrepel.max.overlaps", default = 150))
                   
#                    aes(x = lng, y = lat, label = unigrams), size = 3, max.overlaps = getOption("ggrepel.max.overlaps", default = 150)) 
# 
# View(district_unigram_wlo_3857)
  

ggmap(wien_map) + 
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_label_repel(data = district_unigram_wlo, aes(x = lon, y = lat, label = unigrams), size = 3, max.overlaps = getOption("ggrepel.max.overlaps", default = 150)) 

  coord_sf(crs = st_crs(3857)) + # force the ggplot2 map to be in 3857
  lapply(districts_3857, function(x) geom_sf(data = x, aes(fill = name, alpha = 0.6), inherit.aes = FALSE, show.legend = FALSE)) 
  
  

```